Listening Effort MSC Analysis

### 2024-02-12 MSC 2024 Analysis/msc_analysis.Rmd
small rmd edits
calculated mean speaker intelligibility

>>>>

rm(demo_table, listener_demo)

# Speaker Intelligibility and Phrase Accuracy

## Mean Speaker Intelligibility

data <- rio::import("Cleaned Data/cleaned_data_normed.csv") |>
  # removing trials with missing rep accuracy
  dplyr::mutate(rep_acc = ifelse(rep_acc == "", NA, rep_acc)) |>
  dplyr::filter(!is.na(rep_acc)) |>
  dplyr::mutate(speaker = factor(speaker, levels = c("Control", "ALS")),
                trial_c = trial - 6,
                rep_acc = factor(rep_acc, levels = c("accurate", "inaccurate")))

speaker_acc <- data |>
  dplyr::select(subject, trial, speaker, correct_words, target_number, rep_acc) |>
  dplyr::distinct() |>
  dplyr::mutate(intel = (correct_words/target_number)*100) |>
  dplyr::select(-c(subject, trial, correct_words, target_number)) |>
  tbl_summary(by = speaker,
              type = list(intel ~ "continuous",
                          rep_acc ~ "categorical"),
              statistic = list(all_continuous() ~ "{mean} ({sd})",
                               all_categorical() ~ "{n} ({p}%)"),
              digits = list(everything() ~ c(2)),
              label = list(intel ~ "Intelligibility",
                           rep_acc ~ "Repetition Accuracy")) |>
  as_gt()

speaker_acc

speaker_acc |>
  gt::gtsave("Tables/speaker_intel.html")
